Preliminary results

### 2018-07-05 9thJuly/9thJuly.Rmd
toc added
LCA analysis by day

---
title: "Preliminary results"
output: html_document
---

## Data description

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
setwd("~/Documents/LSHTMproject/Rcode")

@@

library(epiDisplay)
library(plyr)
library(tidyverse)

# Number of subjects per survey year
with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))

# Number of subjects per servey year by gender where Men == 1, Women == 2

with(NDNS, tabpct(SurveyYear, Sex,  graph = FALSE, decimal = 2))

# summary of their age

NDNS %>% 
  group_by(SurveyYear, Sex) %>% 
  summarise(N = n(), MeanAge = mean(Age), SDAge = sd(Age), minAge = min(Age), maxAge = max(Age))

# Dietary data by day

@@

### day 1 data (3 classes)

```{r}

# LCA in day1 -------------------------------------------------------------

# noquote(paste(rep("H", 24), 0:23, sep = ""))
#H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
library(poLCA)
f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)

# lc3$llik #log-likelihood of model
# 
# lc3$P #Estimated class population shares 
# 
# lc3$predclass
```

### day 1 data (Fig.)

@@

library(ggthemr)
a <- (data.frame(lc3$probs))
a$Class <- c("Class1", "Class2", "Class3")

@@

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 45.71%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  41.71%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  12.58%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))
```

```{r echo=FALSE}
library(kableExtra)
dt <- read.csv("../Tablecsv/Modelfit.csv", header = T)
names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")

kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison.") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
```

### Five classes visualisation

@@

lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

a <- (data.frame(lc5$probs))
a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")

@@

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 33.38%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  25.89%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  22.46%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 4:  7.65%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 5:  12.27%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))
```

>>>>

---
title: "Preliminary results"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

# Data description

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
setwd("~/Documents/LSHTMproject/Rcode")

@@

library(epiDisplay)
library(plyr)
library(tidyverse)
library(poLCA)
```

## Number of subjects per survey year

```{r message=FALSE, warning=FALSE, paged.print=FALSE}

with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))

```

## Number of subjects per servey year by gender where Men == 1, Women == 2

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
with(NDNS, tabpct(SurveyYear, Sex,  graph = FALSE, decimal = 2))
```

## Summary of their age 
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
NDNS %>% 
  group_by(SurveyYear, Sex) %>% 
  summarise(N = n(), MeanAge = mean(Age), SDAge = sd(Age), minAge = min(Age), maxAge = max(Age))
```

## Distribution of the dietary data (by Day of Week)

### Day1

```{r}
rm(list=ls(all=TRUE))
load("~/Documents/LSHTMproject/Rcode/NDNSday1_4.Rdata")
with(dta_d1_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
```

### Day2

```{r}
with(dta_d2_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
```

### Day3

```{r}
with(dta_d3_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
```

### Day4

```{r}
with(dta_d4_wide, tab1(DayofWeek, graph = FALSE, decimal = 2))
```

## Distribution of the dietary data (by DayNo)

### Monday

```{r}
rm(list=ls(all=TRUE))
load("~/Documents/LSHTMproject/Rcode/NDNSMon_Sun.Rdata")
with(dta_Mon_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

### Tuesday

```{r}
with(dta_Tue_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

### Wednesday

```{r}
with(dta_Wed_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

### Thursday

```{r}
with(dta_Thurs_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

### Friday

```{r}
with(dta_Fri_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

### Saturday

```{r}
with(dta_Sat_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

### Sunday

```{r}
with(dta_Sun_wide, tab1(DayNo, graph = FALSE, decimal = 2))
```

**The problem of analysing data by day of the week would be that every subject only contributed 3-4 days' data. Therefore, we cannot see one subject's dietary change during a Mon-Sun week.**

## Dietary data by day

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
rm(list=ls(all=TRUE))
load("~/Documents/LSHTMproject/Rcode/NDNSday1_4.Rdata")

vecid <- unique(dfs3$id)

@@

# LCA analyses by day

## Day 1

```{r eval=FALSE}
set.seed(01012)
max_II <- 100000
lc1<-poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
lc2<-poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
lc3<-poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
lc4<-poLCA(f, data=dta_d1_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
lc5<-poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
lc6<-poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
lc7<-poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
lc8<-poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)
```

```{r echo=FALSE}
rm(list=ls(all=TRUE))
load("~/Documents/LSHTMproject/Rcode/day1LCA1_6.Rdata")

library(kableExtra)
# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
lca_results[1,9] <- "---"
kable(lca_results, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (Day 1, n = 6153)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(4,6), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
```

### Day 1 data (Fig. 4 classes)

@@

# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

# a <- (data.frame(lc5$probs))
a <- (data.frame(lc4$probs))
# a <- (data.frame(lc6$probs))

# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
a$Class <- c("Class1", "Class2", "Class3", "Class4")

# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")

@@

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 38.80%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  28.25%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  10.81%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 4:  23.14%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

# 
# ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
# 
# ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
```

### Day 1 data (Fig. 6 classes)

@@

# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

# a <- (data.frame(lc5$probs))
# a <- (data.frame(lc4$probs))
a <- (data.frame(lc6$probs))

# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
# a$Class <- c("Class1", "Class2", "Class3", "Class4")

a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")

@@

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 26.79%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  11.72%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  7.37%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 4:  25.58%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c("Low", "Medium", "High")) +
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c("Low", "Medium", "High")) +
  ylim(c(0,1))
```

## Day 2

```{r eval=FALSE}
set.seed(01012)
max_II <- 100000
lc1<-poLCA(f, data=dta_d1_wide, nclass=1, na.rm = FALSE, nrep=20, maxiter=max_II) #Loglinear independence model.
lc2<-poLCA(f, data=dta_d1_wide, nclass=2, na.rm = FALSE, nrep=20, maxiter=max_II)
lc3<-poLCA(f, data=dta_d1_wide, nclass=3, na.rm = FALSE, nrep=20, maxiter=max_II)
lc4<-poLCA(f, data=dta_d1_wide, nclass=4, na.rm = FALSE, nrep=20, maxiter=max_II) 
lc5<-poLCA(f, data=dta_d1_wide, nclass=5, na.rm = FALSE, nrep=20, maxiter=max_II)
lc6<-poLCA(f, data=dta_d1_wide, nclass=6, na.rm = FALSE, nrep=20, maxiter=max_II)
lc7<-poLCA(f, data=dta_d1_wide, nclass=7, na.rm = FALSE, nrep=20, maxiter=max_II)
lc8<-poLCA(f, data=dta_d1_wide, nclass=8, na.rm = FALSE, nrep=20, maxiter=max_II)

# running time:  31.60514 mins
```

```{r echo=FALSE}
rm(list=ls(all=TRUE))
load("~/Documents/LSHTMproject/Rcode/day2LCA1_6.Rdata")

library(kableExtra)
# dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
# names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")
lca_results[1,9] <- "---"
kable(lca_results, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (Day 2, n = 6153)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(4,6), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; resid.df, residual degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
```

### Day 2 data (Fig. 4 classes)

# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

# a <- (data.frame(lc5$probs))
a <- (data.frame(lc4$probs))
# a <- (data.frame(lc6$probs))

# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
a$Class <- c("Class1", "Class2", "Class3", "Class4")

# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 9.77%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  24.68%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  38.28%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 4:  27.27%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

# 
# ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 5:  18.52%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
# 
# ggplot(a_long[a_long$Class == "Class6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
#  geom_point(size = 3) +
#   geom_line(size = 1.5) +
#   theme(axis.title = element_text(size = 18),
#         axis.text = element_text(size = 18),
#         axis.line = element_line(colour = "black"),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 15)
#         # legend.position = "bottom",
#         # legend.direction = "horizontal"
#         ) +
#   labs(title = "Class 6:  10.02%", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") +
#   scale_color_discrete(labels = c("Low", "Medium", "High")) +
#   ylim(c(0,1))
```

### Day 2 data (Fig. 6 classes)

# lc5 <- poLCA(f, dta_d1_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

# a <- (data.frame(lc5$probs))
# a <- (data.frame(lc4$probs))
a <- (data.frame(lc6$probs))

# a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5")
# a$Class <- c("Class1", "Class2", "Class3", "Class4")

a$Class <- c("Class1", "Class2", "Class3", "Class4", "Class5", "Class6")

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 23.54%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  17.43%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  7.50%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))
